---
title: "Correlation between Flipper Length and Body Mass
on Palmerpenguins Dataset"
author: "Muhammad Hasan Ibrahim"
date: '2022-05-03'
output: html_document
---

## Setting up my environment
Notes: Setting up my R envronment by installing the "tidyverse" and 
"palmerpenguins" packages.

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```

## Visualization
Here we will go throuh a series of visualization

### Flipper and body mass in purple
Here, we plot flipper length againts body mass. The plot shows a positive correlation between flipper length and body mass.
```{r visualize flipper length and body mass in purple}
ggplot(data=penguins)+
  geom_point(mapping=aes(x=flipper_length_mm, y=body_mass_g, color="purple"))+
  geom_smooth(mapping=aes(x=flipper_length_mm, y=body_mass_g))
```

### Flipper and body mass by species
Here, we plot flipper length against body mass by species. The plot shows a positive correlation between flipper length and body mass specified by species.
```{r species}
ggplot(data=penguins)+
  geom_point(mapping=aes(x=flipper_length_mm, y=body_mass_g, shape=species, color="purple"))+
  geom_smooth(mapping=aes(x=flipper_length_mm, y=body_mass_g))
```

### Flipper and body mass by species and sex
Here, we plot flipper length against body mass by species and sex. The plots show positive correlation between flipper length and body mass specified by species and sex.
```{r species and sex}
ggplot(data=penguins)+
  geom_point(mapping=aes(x=flipper_length_mm, y=body_mass_g, color=species, shape=species))+
  facet_wrap(~sex)
```

